Networked Character Devices

### 2011-12-12 report/paper.tex
Fixed spelling errors

We have designed and implemented Network Character Devices (NCD) to
enable a new approach to using and sharing devices. Today, networking 
technology is becoming faster and more reliable at incedible rates. 
More functionality that has been traditionally thought to only be 
feasabily locally accessable can now be pushed to remote
machines. Using client-server operation, our project aims to allow 
a character device (or devices) present on a server to be exported to
a client over a network connection. While character devices come in 
many forms, from Webcams, mice and monitors to USB flash drives and 
external hard drives, NCD works below where these devices are 
interpreted and exports their device file over IP. While designed for
character devices, this generality will actually allow us to export 
any file, which in a *nix system means almost anything on the
system. Being able to dynamically export devices over network
connections suggests a new cloud-like paradigm of device usage where 
locality is required only for reduced latency, which may not be a
concern for certain devices.

When a device is being exported by NCD we would like it to give the
appearence of having essentially ``moved'' the device to the client 
by forbidding user level accesses on the server. This is not part 
of our current iteration of NCD, but it will be included as higher
level functionality is implemented. Aquiring a remote device will be
done through an advertisment protocol that exists in user space so
that details may be supplied about the server and how the connection
should be made (e.g. UDP vs TCP).  After this NCD's functionality on
the client exists in kernel space so as to maintain transparency to
user level operations. Once imported, a device should be accessed just
like a normal local device.  This is acheived by the NCD kernel module
intercepting accesses and sending them out over the network to the
server. On the server, a userspace daemon accesses the physical
device to emulate the client's activity. The overall structure of the
NCD system is present in Figure \ref{fig:system-full}.

@@

Another example of the novel systems that can be built use Network
Charter Devices is a distributed random number generator. Linux has a
fairly robust random number generator built into it and accessible as
a Character Device at \texttt{/dev/random}. This RNG relies on the
local entropy pool (generally filled by human interaction, interrupt
timings, and other high entropy events) to generate random
numbers. This, the speed at which random numbers can be generated is
limited on any single system to the locally available
entropy. This can severely hinder the
performance of systems that require random numbers\footnote{Linux also
provides the \texttt{/dev/urandom} RNG which is a pseudorandom number
generator seeded off teh true
\texttt{/dev/random}. \texttt{/dev/urandom} trades ``randomness'' in
favor of speed. It is thus handy when one just needs to quickly
generate pseudorandom numbers, but is not appropriate for cryptography or
other secure random system.}.

>>>>

We have designed and implemented Network Character Devices (NCD) to
enable a new approach to using and sharing devices. Today, networking 
technology is becoming faster and more reliable at incredible rates. 
More functionality that has been traditionally thought to only be 
feasibly locally accessible can now be pushed to remote
machines. Using client-server operation, our project aims to allow 
a character device (or devices) present on a server to be exported to
a client over a network connection. While character devices come in 
many forms, from Web cams, mice and monitors to USB flash drives and 
external hard drives, NCD works below where these devices are 
interpreted and exports their device file over IP. While designed for
character devices, this generality will actually allow us to export 
any file, which in a *nix system means almost anything on the
system. Being able to dynamically export devices over network
connections suggests a new cloud-like paradigm of device usage where 
locality is required only for reduced latency, which may not be a
concern for certain devices.

When a device is being exported by NCD we would like it to give the
appearance of having essentially ``moved'' the device to the client 
by forbidding user level accesses on the server. This is not part 
of our current iteration of NCD, but it will be included as higher
level functionality is implemented. Acquiring a remote device will be
done through an advertisement protocol that exists in user space so
that details may be supplied about the server and how the connection
should be made (e.g. UDP vs TCP).  After this NCD's functionality on
the client exists in kernel space so as to maintain transparency to
user level operations. Once imported, a device should be accessed just
like a normal local device.  This is achieved by the NCD kernel module
intercepting accesses and sending them out over the network to the
server. On the server, a userspace daemon accesses the physical
device to emulate the client's activity. The overall structure of the
NCD system is present in Figure \ref{fig:system-full}.

@@

Another example of the novel systems that can be built use Network
Charter Devices is a distributed random number generator. Linux has a
fairly robust random number generator built into it and accessible as
a Character Device at \texttt{/dev/random}. This RNG relies on the
local entropy pool (generally filled by human interaction, interrupt
timings, and other high entropy events) to generate random
numbers. This, the speed at which random numbers can be generated is
limited on any single system to the locally available
entropy. This can severely hinder the
performance of systems that require random numbers\footnote{Linux also
provides the \texttt{/dev/urandom} RNG which is a pseudorandom number
generator seeded off the true
\texttt{/dev/random}. \texttt{/dev/urandom} trades ``randomness'' in
favor of speed. It is thus handy when one just needs to quickly
generate pseudorandom numbers, but is not appropriate for cryptography or
other secure random system.}.
